%-------------------------
% Aaysha Ali - Resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

%----------PAGE SETUP----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----------SECTION FORMATTING----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

%----------CUSTOM COMMANDS----------
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & \small #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeCertItem}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \small #3 \\
      \textit{\small #2} & \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, itemsep=2pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

%===========================================
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%===========================================

\begin{document}

%----------HEADING----------
\begin{center}
  {\LARGE \textbf{Aaysha Ali}} \\[4pt]
  \small
  Faridabad, Haryana, India \quad $\cdot$ \quad
  \href{mailto:aliaaysha27@gmail.com}{aliaaysha27@gmail.com} \\[2pt]
  \href{https://linkedin.com/in/aayshaali}{linkedin.com/in/aayshaali} \quad $\cdot$ \quad
  \href{https://github.com/aaysha16}{github.com/aaysha16} \quad $\cdot$ \quad
  \href{https://orcid.org/0009-0005-5832-6542}{orcid.org/0009-0005-5832-6542}
\end{center}

\vspace{-5pt}

%-----------OBJECTIVE-----------
\section{Objective}
\vspace{1pt}
\small{
  Third-year Bachelor of Pharmacy student at Jamia Hamdard with academic training in computational drug design, research methodology, and analytical chemistry. Experienced in molecular docking workflows, HPLC analysis, and scientific writing. Seeking a research-focused postgraduate program or industry internship to apply computational and laboratory skills to drug discovery.
}
\vspace{-2pt}

%-----------EDUCATION-----------
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
  \resumeSubheading
    {Jamia Hamdard}{New Delhi, India}
    {Bachelor of Pharmacy (B.Pharm)}{2023 -- Present}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------RESEARCH AND PUBLICATIONS-----------
\section{Research and Publications}
\vspace{1pt}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Literature Review Publication} $|$ Zenodo Repository}{October 2025}
    \resumeItemListStart
      \resumeItem{Authored a literature review paper analyzing the pharmacological properties and nutraceutical potential of \textit{Tinospora cordifolia} (DOI: \href{https://doi.org/10.5281/zenodo.19390923}{10.5281/zenodo.19390923}).}
      \resumeItem{Synthesized quantitative data on botanical compounds to evaluate safety margins and toxicity profiles from primary pharmacology literature.}
    \resumeItemListEnd
    
  \resumeProjectHeading
    {\textbf{Conference Poster Presentation} $|$ SECON 2025, Jamia Hamdard}{October 2025}
    \resumeItemListStart
      \resumeItem{Designed and presented a scientific poster on ethnopharmacological research at the 12th SFE-India International Convention on ``Traditional Medicine - Ancient \& Modern Concordance''.}
      \resumeItem{Presented and discussed clinical applications of natural products with academic delegates and conference evaluators.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Academic Writing Competition} $|$ Centre of Excellence in Unani Medicine, Jamia Hamdard}{September 2025}
    \resumeItemListStart
      \resumeItem{Authored a review article on traditional dietetics (Unani Aahar) concepts for the Unani Aahar Short Article Writing Competition (Promotional Event for SECON 2025).}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------TECHNICAL TRAINING AND CERTIFICATIONS-----------
\section{Technical Training and Certifications}
\vspace{1pt}
\small{Verification links \& digital credentials portfolio: \href{https://github.com/aaysha16/Certificates}{github.com/aaysha16/Certificates}}
\vspace{2pt}
\resumeSubHeadingListStart

  \resumeCertItem
    {Good Clinical Practice (GCP)}
    {NIDA Clinical Trials Network (6-Hour course; Version 6, valid through June 2029)}
    {June 2026}

  \resumeCertItem
    {Molecular Docking: From Theory to Application}
    {Discovery Boulevard (Hands-on virtual screening, ligand-receptor binding analysis, and docking validation)}
    {June 2026}

  \resumeCertItem
    {HPLC Industrial Visit and Hands-on Training}
    {Arbro Pharmaceuticals Pvt. Ltd. Analytical Division (In collaboration with IPA-Delhi State Branch)}
    {March 2026}

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------LEADERSHIP AND VOLUNTEERING-----------
\section{Leadership and Volunteering}
\vspace{1pt}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Event Volunteer} $|$ Snow Frost Hackathon, Spark Tech AI Hub}{January 2026}
    \resumeItemListStart
      \resumeItem{Coordinated participant check-ins, managed logistical setups, and facilitated operations for technical hackathon tracks.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Conference Volunteer} $|$ 12th Convention of Society for Ethnopharmacology}{October 2025}
    \resumeItemListStart
      \resumeItem{Supported the organizing committee with delegate registration, speaker scheduling, and poster hall logistics during SECON 2025.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Committee Volunteer} $|$ World Pharmacists' Day, SPER Pharmakon Committee}{September 2024}
    \resumeItemListStart
      \resumeItem{Coordinated student registrations and scheduled academic competitions for institutional World Pharmacists' Day events.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Sustainability Volunteer} $|$ Miyawaki Forest Plantation Drive, Cosmo Foundation \& BSF}{October 2024}
    \resumeItemListStart
      \resumeItem{Participated in the planting of a Miyawaki micro-forest at 95 BN BSF Campus (Haryana) to restore local biodiversity.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------SCHOLARSHIPS AND AWARDS-----------
\section{Scholarships and Awards}
\vspace{1pt}
\resumeSubHeadingListStart
  \resumeSubheading
    {Pharmaceutical Industry Merit Scholarship}{New Delhi, India}
    {Smile Foundation}{2023 -- Present}
    \resumeItemListStart
      \resumeItem{Secured a merit-based scholarship for academic excellence, maintained via consistent distinction across all semesters.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------TECHNICAL AND PROFESSIONAL SKILLS-----------
\section{Technical and Professional Skills}
\vspace{1pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt, parsep=0pt]

  \small \item \textbf{Laboratory \& Computational:} HPLC sample preparation, Molecular Docking (AutoDock/Vina), interaction visualization (PyMOL, Discovery Studio), UV-Vis Spectroscopy, basic pharmacognostic assays.

  \small \item \textbf{Research \& Methodology:} Good Clinical Practice (GCP) guidelines, clinical trial regulatory compliance, scientific literature synthesis, literature databases (PubMed, PubChem, ScienceDirect).

  \small \item \textbf{Tools \& Software:} AutoDock/Vina, PyMOL, Discovery Studio Visualizer, ChemDraw, Mendeley (Reference Manager), GraphPad Prism, Python, Microsoft Office (Excel, Word, PowerPoint).

  \small \item \textbf{Languages:} English (fluent), Hindi (proficient), Urdu (native).

\end{itemize}

\end{document}
